---
title: "Exercise_1b"
output: html_document
---

## Initialization

The code underneath initializes the necessary libraries for the subsequent code. I used the libraries ggplot2 and dplyr for the exercise.

```{r libraries}
library(ggplot2)
library(dplyr)
```

## Sampling

The next part of the code, generates the 100 samples from a log-normal distribution with mu=10 and sigma=3.


```{r sampling}
samples <- rlnorm(100, meanlog = 10, sdlog = 3) %>% data.frame(x=.)
```

## Plots

The next part of the code creates a histogram of the distribution, as well as a histogram of the distribution on a log scale.

```{r histogram}
histogram <- ggplot(data=samples, aes(x=x))
histogram + geom_histogram(bins=20, fill="#66CC99") + xlab("x (samples)") + ggtitle("Histogram of log-normal Distribution") + theme(plot.title = element_text(face="bold", size=15, hjust=0.5))

```

And underneath is the code for the distribution on a log scale.

```{r log_histogram}
log_histogram <- ggplot(data=samples, aes(x=x))
log_histogram + scale_x_continuous(trans="log10") + geom_histogram(bins=20, fill="#66CC99") + xlab("x (samples on log scale)") + ggtitle("Histogram of log-normal Distribution on Log Scale") + theme(plot.title = element_text(face="bold", size=15, hjust=0.5))

```
